Numerical Investigation of Viscous Flow Instabilities in Multiphase Heterogeneous Porous Media

### 2018-07-07 Papers/ViscousInstabilities/article_figure1.tex
update

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[h]
\centering
\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of \PN[1]{2} element pairs used in this work. Shaded areas denote control volumes across two contiguous elements. Blue and white circles represent pressure and velocity nodes, respectively.} 
\label{fig:fem_cv}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
\begin{figure}[h]
\centering
%\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively. Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
\label{fig:fem_elem}
\end{figure}
\clearpage

>>>>

%%%%
%%%%  FIGURE 
%%%%
\begin{figure}[h]
\vbox{\vspace{0.cm}
\hbox{\hspace{2cm}
\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\vspace{0.cm}
\hbox{\hspace{5cm}(a)}
\vspace{0.5cm}
\hbox{\hspace{1cm}
\includegraphics[width=.75\textwidth]{./Pics/element_n_2b.pdf}}
\vspace{0.cm}
\hbox{\hspace{3.5cm}(b)\hspace{3cm}(c)}}
%\vbox{\includegraphics[width=.5\textwidth]{./Pics/P1DGP2.pdf}}
\caption{2D representation of \PN[n]{m} element-pairs used in this work: (a) set of \PN[1]{2} FE with shaded areas as control volumes across two contiguous elements (blue and white circles represent pressure and velocity nodes, respectively); Detailed (b) \PN[1]{2} and (c) \PN[1]{1} element-pairs.} 
\label{fig:fem_elem}
\end{figure}
\clearpage

%%%%
%%%%  FIGURE
%%%%
%\begin{figure}[h]
%\centering
%\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_1.pdf}}
%\vbox{\includegraphics[width=.75\textwidth]{./Pics/element_n_2.pdf}}
%\caption{Graphical representation of two different element-types: triangles {\it A} and {\it B} represent \PN[1]{2} and \PN[1]{1} element-pairs, respectively. Porosity $\phi_{i}$, permeability {\bf K}$_{i}$, velocity and pressure are represented in FE space whereas scalar fields (such as saturation, density, viscosity etc) are represented in CV space.}
%\label{fig:fem_elem}
%\end{figure}
%\clearpage
